Very simplified likelihood

### 2024-02-09 inst/very_simplified_likelihood.Rmd
park run using VSL

## Masterchef

Look at the dotchart in the _MasterChef_ part of the `hyper2`
vignette.  We could use a Very Simplified Likelihood to estimate, say,
Laura's BT strength assuming that the other competitors are clones.

>>>>

## Parkrun

```{r readresults}
results <- read.table("parkrun_results.txt",header=TRUE)
results
```

Above we see three parkrun results.  In parkrun number 148, I placed
229 out of a field of 318.

```{r definelikelihood}

L <- function(a,results){
   out <- a*0
   for(i in seq_len(nrow(results))){
   jj <- f_vec_a(a,r=results$place[i]-1,results$runners[i]-1,log=TRUE)
   out <- out + jj
   }
   out[is.infinite(out)] <- NA
   return(out-max(out,na.rm=TRUE))
}
```

```{r calculatelike,cache=TRUE}
a <- seq(from=0.15,to=0.5,by=0.01)
La <- L(a,results)
```

```{r plotlike}
plot(a,La)
abline(h=c(0,-2))
```

```{r splitresults}
supp2 <- function(vec,place,runners){
  a_stirling <- vec[1]
  a_auckland <- vec[2]
  out <- 0
  for(i in 1:3){
    out <- out + f_vec_a(a_stirling,r=place[i]-1,runners[i]-1,log=TRUE)
  }
  for(i in 4:10){
    out <- out + f_vec_a(a_auckland,r=place[i]-1,runners[i]-1,log=TRUE)
  }
  return(out)
}
```

```{r}
print(supp2(c(0.1,0.3),results$place,results$runners))
supp2(c(0.1,0.3),results$place,results$runners)
x <- seq(from=0.1,to=0.5,by=0.005)
jj <- as.matrix(expand.grid(x,x))
L <- apply(jj,1,supp2,results$place,results$runners)
L <- L - max(L,na.rm=TRUE)
L <- matrix(L,length(x),length(x))
par(pty='s')
contour(x,x,L,asp=1,xlim=range(x),ylim=range(x))
abline(0,1)
```
